EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Repeated reference.

A new feature in \EVOSUITE is the use of Mockito mock
classes~\cite{ICST_Mocking17}. After a certain percentage of the
search budget has passed, \EVOSUITE starts considering the use of mock
objects instead of real classes. Only branches that cannot be covered
without mocks will result in tests with mock objects in the end. We
further added frequency based weighting to constants for
seeding~\cite{sakti2015instance}, and included extensions to support
Java Enterprise Edition features~\cite{arcuri2016java}. Besides these
changes, several bug fixes were applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{ase14_environment}.

>>>>

A new feature in \EVOSUITE is the use of Mockito mock
classes~\cite{ICST_Mocking17}. After a certain percentage of the
search budget has passed, \EVOSUITE starts considering the use of mock
objects instead of real classes. Only branches that cannot be covered
without mocks will result in tests with mock objects in the end. We
further added frequency based weighting to constants for
seeding~\cite{sakti2015instance}, and included extensions to support
Java Enterprise Edition features~\cite{arcuri2016java}. Besides these
changes, several bug fixes were applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{arcuri2014automated}.
